Fast approximate Bayesian inference of HIV indicators using PCA adaptive Gauss-Hermite quadrature

### 2023-07-03 src/docs_paper/appendix.Rmd
Add plot of node marginal quantiles within NUTS posterior samples

@@

>>>>

```{r nodes-quantiles-sd, fig.cap="Standard deviations of the quantiles of the quadrature nodes within the NUTS posterior draws varied substantially, in accordance with the marginal standard deviations shown in Figure \\ref{fig:marginal-sd}."}
knitr::include_graphics("depends/nodes-quantiles-sd.png")
```

@@

Add here plots and description of the estimated normalising constant for different PCA-AGHQ settings.

### 2023-07-03 src/docs_paper/paper.Rmd
Add plot of node marginal quantiles within NUTS posterior samples

```{r mean-sd, fig.cap="PCA-AGHQ modestly improves estimation of the posterior mean, and substantially improves estimation of the posterior standard deviation, as compared with TMB."}
knitr::include_graphics("depends/mean-sd-alt.png")
```

>>>>

```{r mean-sd, fig.cap="PCA-AGHQ modestly improves estimation of the posterior mean, and substantially improves estimation of the posterior standard deviation, as compared with TMB."}
knitr::include_graphics("depends/mean-sd-alt-latent.png")
```
